Prediction model for PMI using ROSMAP Reprocessed RNASeq

### 2016-06-11 code/Rmd/PredictPMI.Rmd
Minor fix

@@

# Fit linear model using estimated weights and calculate BIC's
BIC.WOPMI = sapply(1:dim(VOOM.ADJUSTED.GENE_EXPRESSION$E)[1], function(gene){
  y = VOOM.ADJUSTED.GENE_EXPRESSION$E[gene,]
  w = VOOM.ADJUSTED.GENE_EXPRESSION$weights[gene,]
  x = DM1$design
  obj = lm(y~0+., data = cbind(x,data.frame(y=y)), weights = w)
  BIC(obj)
})
names(BIC.WOPMI) = rownames(VOOM.ADJUSTED.GENE_EXPRESSION$E)
```
### Predict PMI
```{rpredict.pmi}
# Extract features that show improvement in the model with pmi when compared to without pmi
genes = rownames(VOOM.ADJUSTED.GENE_EXPRESSION$E)[which((BIC.WOPMI-BIC.WPMI) >= 6)]

@@

# Store features in synapse (union of both the models)
tmp = setdiff(unique(c(coeff1$Coefficients, coeff2$coefficients)), '(Intercept)')
write.table(tmp, file = 'features.tsv', sep = '\n', row.names = F, quote=F)
obj = File('features.tsv', name = 'Predictors of PMI', parentId = CODE$properties$id)
obj = synStore(obj, used = as.character(ALL_USED_IDs), executed = thisFile, 
               activityName = activityName, activityDescription = activityDescription)
```

>>>>

library(doParallel)
library(foreach)

cl = makeCluster(14)
registerDoParallel(cl)

@@

# Fit linear model using estimated weights and calculate BIC's
BIC.WOPMI = sapply(1:dim(VOOM.ADJUSTED.GENE_EXPRESSION$E)[1], function(gene){
  y = VOOM.ADJUSTED.GENE_EXPRESSION$E[gene,]
  w = VOOM.ADJUSTED.GENE_EXPRESSION$weights[gene,]
  x = DM1$design
  obj = lm(y~0+., data = cbind(x,data.frame(y=y)), weights = w)
  BIC(obj)
})
names(BIC.WOPMI) = rownames(VOOM.ADJUSTED.GENE_EXPRESSION$E)
```
### Predict PMI
```{r predict.pmi, fig.height=6, fig.width=6}
# Extract features that show improvement in the model with pmi when compared to without pmi
genes = rownames(VOOM.ADJUSTED.GENE_EXPRESSION$E)[which((BIC.WOPMI-BIC.WPMI) >= 6)]

@@

# Store features in synapse (union of both the models)
tmp = setdiff(unique(c(coeff1$Coefficients, coeff2$coefficients)), '(Intercept)')
write.table(tmp, file = 'features.tsv', sep = '\n', row.names = F, quote=F)
obj = File('features.tsv', name = 'Predictors of PMI', parentId = CODE$properties$id)
obj = synStore(obj, used = as.character(ALL_USED_IDs), executed = thisFile, 
               activityName = activityName, activityDescription = activityDescription)
stopCluster(cl)
```
